% !TeX spellcheck = en_US
\documentclass{beamer}
\usepackage[latin1]{inputenc}
\usepackage{dsfont}
\usepackage{color}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{arrows}

% % % % % FRAME STYLE

% NEW
%\usetheme{Frankfurt}

%\setbeamertemplate{navigation symbols}{}
%\setbeamertemplate{frametitle}[default][center]

% OLD
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{frametitle}{\vspace{5mm}\hspace{0mm}\insertframetitle}
%\setbeamertemplate{frametitle}[default][center]
\setbeamertemplate{footline}{\hfill\insertframenumber/\inserttotalframenumber\hspace{5mm}\vspace{5mm}}
\AtBeginSection[]
{
	\begin{frame}
		\frametitle{Agenda}
		\tableofcontents[currentsection]
	\end{frame}
}

\usefonttheme{structurebold}
\usecolortheme{dove}

% % % % % CUSTOM COMMANDS
\newcommand{\Empty}{\mbox{$\varnothing$}}
\newcommand{\NotEmpty}{\mbox{$\neg\varnothing$}}
\newcommand{\ToDo}{\textcolor{red}{TODO}}
\newcommand{\Highlight}[1]{\textcolor{purple}{#1}}
% % % % % FRAMES

\begin{document}

	\title{Qualitative Spatial Reasoning over Line-Region Relations}
	\author{Leena and Sibel}
	\date{Knowledge Representation\\Seminar Presentation}
	
	\begin{frame}
		\titlepage
	\end{frame}
	
	\section{Motivation}
	\include{motivation}
	
	\section{9-Intersection}	
	\include{9-intersection}
	
	\section{Snapshot Model}	
	\include{snapshot_model}
	
	\section{Smooth-Transition Model}	
	\include{smooth_transitions}	
	
	\section{Evaluation}	
	\include{evaluation}
	
	\section{Summary}
	\include{summary}
	
	\begin{comment}
		- citing style chicago
		- sorted by relevance
	\end{comment}
	\begin{frame}[allowframebreaks]{References}
		\begin{itemize}
			\item Egenhofer, Max J., and David M. Mark. "Modelling conceptual neighbourhoods of topological line-region relations." \textit{International journal of geographical information systems} 9.5 (1995): 555-565.
			
			\item Mark, David M., and Max J. Egenhofer. "Modeling spatial relations between lines and regions: combining formal mathematical models and human subjects testing." Cartography and geographic information systems 21.4 (1994): 195-212.
			
			\item Egenhofer, Max J., and A. Rashid Shariff. "Metric details for natural-language spatial relations." \textit{ACM Transactions on Information Systems (TOIS)} 16.4 (1998): 295-321.
			%Max J Egenhofer, A. B. Metric details for natural language spatial relations ACM Transactions on Information Systems, 1998

			\item Talmy, Leonard. \textit{How language structures space}. Springer US, 1983.
			%Talmy, L. Herbert L. Pick Jr, L. P. A. (Ed.) How lnaguage structures space Springer, 1983
			
			\item Clark, Herbert H. "Space, time, semantics, and the child." (1973).

			\item Moore, Timothy E. "Cognitive Development and the Acquisition of Language." (1973).
			%Clark, H. H. Space, time, semantics and the child Cognitive development and acquisition of language, 1973
		\end{itemize}
	\end{frame}
	
\end{document}